Efficient code generation for loop-free IR

### 2024-05-06 paper.tex
add figure

The old generator also allows statements to be emitted inside irrelevant loops, which may sometimes yield incorrect results.
\end{enumerate}
\iffalse
We compare the generated code of both the old and the new code generator on the Rhyme solution for advent of code day5-part1. The old code generator already generates decent code, and the new code generator generates similar code to the old code generator in most test cases. The old generator only fails at certain complex applications. Therefore, we choose advent of code day5-part1 for comparison as the old code generator fails to schedule all statements for this application and uses repeated generators to generate the remaining IR.\par
The JavaScript code that the old code generator generates is 223 lines while the new code generator only generates 134 lines. This is $39.9\%$ reduce in the code size. The new code generator manages to merge more statements' loops together, therefore reduces the code size. When executing on the puzzle inputs from advent of code, the execution time reduces by $21.6\%$.\par
In conclusion, compared with the old code generator, our new code generator generates more efficient code by aggressively performing loop fusion at code generation time.
\fi
We compare the generated code of both the old and the new code generator on the Rhyme solution for Advent of Code day5-part1. The old code generator already generates decent code, and the new code generator generates similar code to the old code generator in most test cases. The old generator only fails at certain complex applications. Therefore, we choose Advent of Code day5-part1 for comparison as the old code generator fails to schedule all statements for this application and uses repeated generators to generate the remaining IR.\par

The JavaScript code that the old code generator generates is 223 lines while the new code generator only generates 134 lines. This is a $39.9\%$ reduction in the code size. The new code generator manages to merge more statements' loops together, therefore reducing the code size. When executing on the puzzle inputs from Advent of Code, the execution time reduces by $21.6\%$.\par

@@

\section{Conclusion}\label{conclusion}
\iffalse
In this paper, we present an efficient code generation algorithm for loop-free, branch-free Rhyme IR. We present the constraints and dependencies that the code generator must follow in order to guarantee the correctness of generated code for Rhyme IR. We also present a heuristic guided loop scheduling algorithm that can achieve loop fusion at code generation time.
\fi
In this paper, we present an efficient code generation algorithm for loop-free, branch-free Rhyme IR. We present the constraints and dependencies that the code generator must follow to guarantee the correctness of the generated code for Rhyme IR. We also present a heuristic-guided loop scheduling algorithm that can achieve loop fusion at code generation time.
\newpage
\bibliographystyle{acm}
\bibliography{paper}
\end{document}
\endinput

>>>>

The old generator also allows statements to be emitted inside irrelevant loops, which may sometimes yield incorrect results.
\end{enumerate}
\iffalse
We compare the generated code of both the old and the new code generator on the Rhyme solution for advent of code day5-part1. The old code generator already generates decent code, and the new code generator generates similar code to the old code generator in most test cases. The old generator only fails at certain complex applications. Therefore, we choose advent of code day5-part1 for comparison as the old code generator fails to schedule all statements for this application and uses repeated generators to generate the remaining IR.\par
The JavaScript code that the old code generator generates is 223 lines while the new code generator only generates 134 lines. This is $39.9\%$ reduce in the code size. The new code generator manages to merge more statements' loops together, therefore reduces the code size. When executing on the puzzle inputs from advent of code, the execution time reduces by $21.6\%$.\par
In conclusion, compared with the old code generator, our new code generator generates more efficient code by aggressively performing loop fusion at code generation time.
\fi
We compare the generated code of both the old and the new code generator on the Rhyme solution for Advent of Code day5-part1. The old code generator already generates decent code, and the new code generator generates similar code to the old code generator in most test cases. The old generator only fails at certain complex applications. Therefore, we choose Advent of Code day5-part1 for comparison as the old code generator fails to schedule all statements for this application and uses repeated generators to generate the remaining IR.\par
\begin{figure}[H]
  \centering
      \includegraphics[scale=0.57]{evaluation.pdf}
      \caption{Old vs New code generator}
      \label{evaluationpic}
  \end{figure}
As shown in Figure \ref{evaluationpic}, the JavaScript code that the old code generator generates is 223 lines while the new code generator only generates 134 lines. This is a $39.9\%$ reduction in the code size. The new code generator manages to merge more statements' loops together, therefore reducing the code size. When executing on the puzzle inputs from Advent of Code, the execution time reduces by $21.6\%$.\par

@@

\section{Conclusion}\label{conclusion}
\iffalse
In this paper, we present an efficient code generation algorithm for loop-free, branch-free Rhyme IR. We present the constraints and dependencies that the code generator must follow in order to guarantee the correctness of generated code for Rhyme IR. We also present a heuristic guided loop scheduling algorithm that can achieve loop fusion at code generation time.
\fi
In this paper, we present an efficient code generation algorithm for loop-free, branch-free Rhyme IR. We present the constraints and dependencies that the code generator must follow to guarantee the correctness of the generated code for Rhyme IR. We also present a heuristic-guided loop scheduling algorithm that can achieve loop fusion at code generation time.
%\newpage
\bibliographystyle{acm}
\bibliography{paper}
\end{document}
\endinput
